The fifteen year struggle of decentralizing privacy-enhancing technology

### 2014-03-26 paper.tex
Fixed minor typos + changed 'Directory Servers' to 'directory servers'

		To mitigate these concerns, Directory Servers were introduced to Tor during its reimplementation. These Directory Servers keep a redundant central consensus about the network. They act as HTTP servers to which Tor nodes can publish signed information about themselves. Tor clients can in turn download this information, as seen in figure \ref{fig:tor_layout}.

		The information distributed by the Directory Servers is signed. The keys to verify these signatures are preloaded in the Tor software, along with the list of Directory Servers. This implies trust by the Tor client in the Directory Servers.

@@

	\subsection{Key exchange}
		With a decentralized network, using a centralized authority for managing the keys is not possible. This means that for secure communication, peers have to exchange the keys directly with each other, without a trusted party between them. Diffie-Hellman is a very popular algorithm for exchanging keys between two parties. It is used in the circuit creation in Onion Routing (see section \ref{ss:tor_circuit}) for example. However, it is possible for an adversary to manipulate the keys send between two parties, making the protocol vulnerable to a man-in-the-middle attack. This weakness makes it possible for an adversary to decrypt all messages sent between the two parties.

@@

	\subsection{NISAN} % 2009
		NISAN, or Network Information Service for Anonymization Networks \cite{panchenko2006nisan}, is an anonymization network which implements a distributed node discovery. Not only does a central node administrator (the Directory Server in Tor) imply trust in those servers, Panchenko et al. also argue that a central node administration (the Directory Server in Tor) does not scale. The current directory server protocol was already improved two times to reduce bandwidth costs, with a fairly low amount of users.

@@

		Instead of the Directory Servers, it uses a DHT and a new Neighbourhood Authority. The DHT is a combination of Kademlia DHT and Myrmic DHT. Kademlia DHT was chosen because it is already widely used and it has proven itself for a large number of users.

		The Myrmic DHT runs on top of Kademlia, and introduces the Neighbourhood Authority. This authority issues certificates to nodes that participate in the DHT, but it does not participate in the DHT itself. The Neighbourhood Authority makes this solution not a fully decentralized one, but its role is a lot smaller than the current Directory Servers. This does not solve the trust issue, but it does solve the scalability issue.

@@

	%Redecentralize.org is a project that describes itself with the aim to \textquoteleft start of a new information revolutions\textquoteright~by \textquoteleft bringing decentralized in the hands of billions\textquoteright~\cite{aboutredecentralizeorg}. One of the ways they do this, is by maintaining a Github repository\footnote{Found at https://github.com/redecentralize/alternative-internet} with projects that in some way help to decentralize the internet.

>>>>

		To mitigate these concerns, directory servers were introduced to Tor during its reimplementation. These directory servers keep a redundant central consensus about the network. They act as HTTP servers to which Tor nodes can publish signed information about themselves. Tor clients can in turn download this information, as seen in figure \ref{fig:tor_layout}.

		The information distributed by the directory servers is signed. The keys to verify these signatures are preloaded in the Tor software, along with the list of directory servers. This implies trust by the Tor client in the directory servers.

@@

	\subsection{Key exchange}
		With a decentralized network, using a centralized authority for managing the keys is not possible. This means that for secure communication, peers have to exchange the keys directly with each other, without a trusted party between them. Diffie-Hellman is a very popular algorithm for exchanging keys between two parties. It is used in the circuit creation in Onion Routing (see section \ref{ss:tor_circuit}) for example. However, it is possible for an adversary to manipulate the keys exchanged between two parties, making the protocol vulnerable to a man-in-the-middle attack. This weakness makes it possible for an adversary to decrypt all messages sent between the two parties.

@@

	\subsection{NISAN} % 2009
		NISAN, or Network Information Service for Anonymization Networks \cite{panchenko2006nisan}, is an anonymization network which implements a distributed node discovery. Not only does a central node administrator (the directory server in Tor) imply trust in those servers, Panchenko et al. also argue that a central node administration (the directory server in Tor) does not scale. The current directory server protocol was already improved two times to reduce bandwidth costs, with a fairly low amount of users.

@@

		Instead of the directory servers, it uses a DHT and a new Neighbourhood Authority. The DHT is a combination of Kademlia DHT and Myrmic DHT. Kademlia DHT was chosen because it is already widely used and it has proven itself for a large number of users.

		The Myrmic DHT runs on top of Kademlia, and introduces the Neighbourhood Authority. This authority issues certificates to nodes that participate in the DHT, but it does not participate in the DHT itself. The Neighbourhood Authority makes this solution not a fully decentralized one, but its role is a lot smaller than the current directory servers. This does not solve the trust issue, but it does solve the scalability issue.

@@
